---
title: "About"
format: html
jyml:
---

My name is Seth, I am a student at Zicklin, Baruch's Business School. I am currently on track to receive my Master's in Statistics with a focus in Data Science at the end of the Fall 2025 semester.

```{r}
#| echo: false
#| message: false
#| warning: false

if(!require("leaflet")){
  options(repos=c(CRAN="https://cloud.r-project.org"))
  install.packages("leaflet")
  stopifnot(require("leaflet"))
}

baruch_longitude <- -73.98333
baruch_latitude  <- +40.75028

leaflet() |>
  addTiles() |>
  setView(baruch_longitude, baruch_latitude, zoom=17) |>
  addPopups(baruch_longitude, baruch_latitude, 
            "I am a Master's student at <b>Baruch College</b>!")
```

This is a page created for my STA 9890 class which contains two research reports on Machine Learning and my final prediction competition project for the class, where I finished 15th place out of 31 other students (in 27 groups).

```{r}
#| include: false
1+1
```
--------------
  Last Updated: `r format(Sys.time(), "%A %m %d, %Y at %H:%M%p")`